IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/intro.tex
rm
bringing haskell back
haskell back in intro

%In the alternative \textit{coarse-grained} approach to IFC,
The Operating Systems community has tackled this challenge (e.g.,
in~\cite{Zeldovich:2006}) by taking a \textit{coarse-grained} approach
to IFC: dividing an application into coarse computational units,
each with a single label dictating its security policy, and only
monitoring communication between them.
%Only communication between isolated computational units must be tracked.
%A recent system named COWL~\cite{swapi} adds IFC to the
%browser by identifying \emph{web workers} as an existing computational
%unit.  Communication between workers is mediated using
%IFC to ensure non-interference, preventing sensitive workers from
%influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages when
compared to the fine-grained approaches typically employed by language-based systems.
First, adding IFC does not require intrusive changes to an
existing programming language, thereby also allowing
the reuse of existing programs.  Second, it has a small
runtime overhead because checks need only
be performed at isolation boundaries
instead of (almost) every program instruction~(e.g.,~\cite{JSFlow}).
%, compared to fine-grained
%systems were the runtime overhead can be impractical~\cite{JSFlow}.
Finally, by associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the security guarantees of the
system, without reasoning about most of the
technical details of the semantics of the underlying programming language.
\Red{ds: this last senstence needs work}

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  dynamic information flow control language free of non-IFC constructs.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism and show a class of restrictions on
  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
  \item We have implemented an IFC system based on these semantics
  for Node.js, and we connect our formalism to another implementation
  based on this work
  for client-side JavaScript in~\cite{swapi}.
  Furthermore, we outline an implementation for the C programming
  language.
  (Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
%  \item We describe ways to enrich the core IFC language with
%  more advanced concepts such as labeled values, labeled references, or a
%  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}

>>>>

%In the alternative \textit{coarse-grained} approach to IFC,
The Operating Systems community has tackled this challenge (e.g.,
in~\cite{Zeldovich:2006}) by taking a \textit{coarse-grained} approach
to IFC: dividing an application into coarse computational units,
each with a single label dictating its security policy, and only
monitoring communication between them.
%Only communication between isolated computational units must be tracked.
%A recent system named COWL~\cite{swapi} adds IFC to the
%browser by identifying \emph{web workers} as an existing computational
%unit.  Communication between workers is mediated using
%IFC to ensure non-interference, preventing sensitive workers from
%influencing the computation of less sensitive workers.
This coarse-grained approach provides a number of advantages when
compared to the fine-grained approaches typically employed by language-based systems.
First, adding IFC does not require intrusive changes to an
existing programming language, thereby also allowing
the reuse of existing programs.  Second, it has a small
runtime overhead because checks need only
be performed at isolation boundaries
instead of (almost) every program instruction~(e.g.,~\cite{JSFlow}).
%, compared to fine-grained
%systems were the runtime overhead can be impractical~\cite{JSFlow}.
Finally, by associating
a single security label with the entire computational unit simplifies
understanding and reasoning about the security guarantees of the
system, without reasoning about most of the
technical details of the semantics of the underlying programming language.

@@

Our contributions can be summarized as follows:
\begin{itemize}
  \item We give formal semantics for a core coarse-grained
  dynamic information flow control language free of non-IFC constructs.
  We then show how a large class of target languages can be combined
  with this IFC language and prove that the result provides
  non-interference. (Sections~\ref{sec:retrofit} and \ref{sec:formal})
  \item We provide a proof technique to show the non-interference
  of a concrete semantics for a potentially optimized IFC language
  by means of an isomorphism and show a class of restrictions on
  the IFC language that preserves non-interference. (Sections~\ref{sec:concrete})
  \item We implemented an IFC system based on these semantics
  for Node.js, and we connect our formalism to another implementation
  based on this work for client-side JavaScript~\cite{swapi}.
  Furthermore, we outline an implementation for the C programming
  language and describe improvements to the Haskell LIO system that
  resulted from this framework.
  (Section~\ref{sec:real})
%  \item We show how to extend the Matthews-Findler method from just
%  languages that are not simply expressions evaluating to values,
%  but may be collections of threads executing nondeterministically.
%  \item We describe ways to enrich the core IFC language with
%  more advanced concepts such as labeled values, labeled references, or a
%  notion of clearance. (Section~\ref{sec:extensions})
\end{itemize}
